Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Revise the methodology section after proof-reading #1

% Sample
We estimate equation (\ref{gdp}) with OLS, by using the balanced panel of countries around the world from 1992 to 2013. The balanced panel ensures no compositional bias in the estimation of year fixed effects, $\eta_t$, important parameters to recover $y_{i,t}$ for unrecognized states (see below). 
The sample of countries excludes the parent countries of unrecognized states (i.e.\ Georgia, Azerbaijan, and Moldova) because we will validate our predicted values of real GDP growth against the actual real GDP growth rates in these three countries.
Standard errors are clustered both at the territory level and at the year level with the multi-way cluster robust inference method (Cameron et al.\ 2011).%
\footnote{Due to multicollinearity, we need to drop one dummy for either a country or a year when we estimate equation (\ref{gdp}). We drop the dummy for year 1992.}

>>>>

% Sample
We estimate equation (\ref{gdp}) with OLS, by using the balanced annual panel of countries around the world from 1992 to 2013. 
The balanced panel ensures no compositional bias in the estimation of year fixed effects, $\eta_t$, important parameters to recover the annual growth in $y_{i,t}$ for unrecognized states (see below). 
The sample of countries excludes the parent countries of unrecognized states (i.e.\ Georgia, Azerbaijan, and Moldova) because we will validate our predicted values of real GDP growth against the actual real GDP growth rates in these three countries.
Standard errors are clustered both at the territory level and at the year level with the multi-way cluster robust inference method (Cameron et al.\ 2011).%
\footnote{Due to multicollinearity, we need to drop one dummy for either a country or a year when we estimate equation (\ref{gdp}). We drop the dummy for year 1992. Consequently, year fixed effects, $\eta_{t}$, are interpreted as the average differences in real GDP in each year relative to the 1992 level.}
